\textsf{Are frontier models superhuman chemists?}

### 2024-03-16 src/tex/ms.tex
manuscript compiles
pin env to make embeddings work

While many of the existing benchmarks are designed around \gls{mcq}, this does not reflect the reality of chemistry education and research.
For this reason, \chembench samples both \gls{mcq} and open-ended questions in a balanced way (\variable{output/mcq_questions.txt} \gls{mcq} questions vs. \variable{output/non_mcq_questions.txt} open-ended questions).
As one might expect, most questions are difficult to read according to the Flesch–Kincaid readability test (\variable{output/flesch_kincaid_reading_ease.txt}).\cite{kincaid1975derivation}

@@

@@

\appendix
\input{appendix.tex}

>>>>

\begin{figure}
    \centering
    \includegraphics{figures/question_diversity.pdf}
    \caption{\textbf{Principal component projection of embeddings of questions in the \chembench corpus.}}
    \label{fig:question_diversity}
    \script{plot_question_diversity.py}
\end{figure}

While many of the existing benchmarks are designed around \gls{mcq}, this does not reflect the reality of chemistry education and research.
For this reason, \chembench samples both \gls{mcq} and open-ended questions (\variable{output/mcq_questions.txt} \gls{mcq} questions vs. \variable{output/non_mcq_questions.txt} open-ended questions).
As one might expect, most questions are difficult to read according to the Flesch–Kincaid readability test (\variable{output/flesch_kincaid_reading_ease.txt}).\cite{kincaid1975derivation}

@@

\appendix
\section{Appendix}
\input{appendix.tex}

@@
